---
title: "Untitled"
author: "Emorie D Beck"
date: "4/5/2017"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.kable.NA = '')
source("~/Box/network/other projects/swb networks/02_graphicalVAR-testing.R")
```

```{r}
Mode <- function(x) {
  ux <- unique(x)
  ux <- ux[!is.na(ux)]
  ux[which.max(tabulate(match(x, ux)))]
}
```


# Workspace  
## Packages  
```{r}
library(qgraph)
library(igraph)
library(glasso)
library(mlVAR)
library(graphicalVAR)
library(knitr)
library(kableExtra)
library(readxl)      # read excel files
library(Rmisc)
library(psych)
library(magrittr)
library(data.table)
library(tidyverse)
library(Matrix)
library(RColorBrewer)

wd <- "~/Box/network/other projects/swb networks"
data_path <- "/Volumes/Emorie Beck/data"
```

## Codebooks  
```{r}
# list of all codebook sheets
sheets <- sprintf("%s/02_codebooks/01_master-codebook-2021-03-17.xlsx", wd) %>% excel_sheets()

# function for reading in sheets
read_fun <- function(x){
  sprintf("%s/02_codebooks/01_master-codebook-2021-03-17.xlsx", wd) %>% read_xlsx(., sheet = x)
}

# read in sheets and index source
codebook <- tibble(
  study = sheets,
  codebook = map(study, read_fun)
)
```

## Data  
### GSOEP  
#### Load Data  
```{r gsoep clean fun}
gsoep_read_fun <- function(Year, WL){
  print(Year)
  old.names <- (gsoep_codebook %>% filter(year == Year | category == "proc"))$orig_itemname 
  p <- sprintf("%s/gsoep/%sp.sav", data_path, WL) %>% haven::read_sav(.) %>%
    full_join(sprintf("%s/gsoep/%skind.sav", data_path, WL) %>% haven::read_sav(.)) %>%
    full_join(sprintf("%s/gsoep/%spequiv.sav", data_path, WL) %>% haven::read_sav(.)) %>%
    full_join(sprintf("%s/gsoep/%spgen.sav", data_path, WL) %>% haven::read_sav(.)) %>%
    full_join(sprintf("%s/gsoep/%spkal.sav", data_path, WL) %>% haven::read_sav(.)) %>%
    select(persnr, hhnr, one_of(old.names)) %>%
    gather(key = orig_itemname, value = value, -persnr, -hhnr, na.rm = T)
  
 ph <- sprintf("%s/gsoep/%shbrutto.sav", data_path, WL) %>% haven::read_sav(.) %>%
    full_join(sprintf("%s/gsoep/%sh.sav", data_path, WL) %>% haven::read_sav(.)) %>%
    select(hhnr, one_of(old.names))
 if(ncol(ph) != 0){
   p <- ph %>%
    gather(key = orig_itemname, value = value, -hhnr, na.rm = T) %>%
    full_join(p %>% select(persnr, hhnr) %>% distinct()) %>%
    full_join(p)
 }
   return(p)
}
```

```{r gsoep codebook}
gsoep_codebook <- (codebook %>% filter(study == "gsoep"))$codebook[[1]] %>%
  mutate(orig_itemname = str_to_lower(orig_itemname)
         , orig_itemname = str_remove_all(orig_itemname, "[:space:]"))
gsoep_codebook
```

```{r gsoep data, eval = F}
gsoep <- gsoep_codebook %>% 
  select(wave, waveletter, year) %>%
  filter(complete.cases(.)) %>%
  distinct() %>%
  arrange(year) %>%
  filter(year < "2018") %>%
  mutate(data = map2(year, waveletter, gsoep_read_fun)) 

old.names <- unique(gsoep_codebook$orig_itemname)

gsoep_long <- gsoep %>% 
  unnest(data) %>%
  select(-wave, -waveletter, -hhnr) %>%
  full_join(sprintf("%s/gsoep/bioparen.sav", data_path) %>% 
  haven::read_sav(.) %>%
  select(one_of(old.names)) %>%
  gather(key = orig_itemname, value = value, -persnr, na.rm = T) %>%
  mutate(year = 0)) %>%
  rename(SID = persnr)

save(gsoep, file = sprintf("%s/01_data/01_clean/gsoep_raw.RData", wd))
rm(gsoep)
```

#### Recoding  
```{r gsoep recode, eval = F}
# join data with recoding info 
gsoep_recode <- gsoep_codebook %>%
  filter(category %in% c("overall", "domain", "correlates")) %>%
  select(category, name, itemname, wave, year, orig_itemname, reverse_code:long_rule) %>%
  group_by(category, name) %>% 
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% left_join(gsoep_long))) 

# recode 
recode_fun <- function(rule, y, year){
  x <- y$value
  if(!is.na(rule)){y$value <- eval(parse(text = rule))}
  return(y)
}

gsoep_recode <- gsoep_recode %>% 
  mutate(data = map(data, ~(.) %>% 
    group_by(recode, year) %>%
    nest() %>%
    ungroup() %>%
    mutate(data = pmap(list(recode, data, year), recode_fun)) %>%
    unnest(data) %>%
    mutate(value = ifelse(value < 0 | is.nan(value) | is.infinite(value), NA, value))))


# reverse code 
gsoep_recode <- gsoep_recode %>%
  mutate(data = map(data, ~(.) %>%
    mutate(value = ifelse(reverse_code == "no" | is.na(reverse_code), value, 
                        reverse.code(-1, value, mini = mini, maxi = maxi)))))

fun_call <- function(x, rule){
    switch(rule,
           average = mean(x, na.rm = T),
           mode = Mode(x)[1],
           sum = sum(x, na.rm = T),
           skip = unique(x)[1],
           select = unique(x)[1],
           max = max(x, na.rm = T),
           min = min(x, na.rm = T))
  }
```

#### Satisfaction  
```{r, eval = F}
gsoep <- gsoep_recode %>%
  filter(category != "correlates") %>%
  unnest(data) %>%
  select(name, year, SID, value) %>%
  filter(complete.cases(.)) %>%
  group_by(name, year, SID) %>%
  summarize(value = mean(value)) %>%
  ungroup() %>%
  pivot_wider(names_from = "name", values_from = "value") %>%
  group_by(SID) %>%
  filter(n() >= 5) %>%
  ungroup()

gsoep_years <- gsoep %>%
  group_by(SID) %>%
  filter(year == median(year)) %>%
  ungroup() %>%
  select(m_year = year, SID)
```

#### Correlates  

```{r, eval = F}
gsoep_corr <- gsoep_recode %>%
  filter(category == "correlates") %>%
  select(-category) %>%
  mutate(data = map(data, ~(.) %>% 
      filter(!is.na(value)) %>%
      mutate(comp_rule = ifelse(is.na(comp_rule), "skip", comp_rule)) %>%
      group_by(comp_rule, SID, year, long_rule) %>%
      nest() %>%
      ungroup() %>%
      mutate(data = map2(data, comp_rule, ~fun_call((.x)$value, .y))) %>%
      unnest(data) %>%
      right_join(gsoep_years) %>%
      filter(year <= m_year)
      # summarize(value = fun_call(value, comp_rule)) %>%
      # ungroup() %>% 
      # mutate(value = ifelse(is.infinite(value) | is.nan(value), NA, value))
      ))

comp_fun <- function(d, rule, p_year){
  print(paste(rule, p_year))
  d %>%
    group_by(SID, name) %>%
    summarize(value = fun_call(data, rule)) %>%
    ungroup() %>%
    distinct()
}

# composite ACROSS years
gsoep_corr <- gsoep_corr %>%
  unnest(data) %>%
  mutate(long_rule = ifelse(is.na(long_rule), "skip", long_rule)) %>%
  filter(year <= m_year) %>%
  group_by(m_year, long_rule) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = pmap(list(data, long_rule, m_year), comp_fun)) %>%
  unnest(data) %>%
  mutate(value = ifelse(is.infinite(value) | is.nan(value), NA, value)) %>%
  select(-long_rule) %>%
  spread(name, value) %>%
  filter(!is.na(SID))%>%
  mutate(yearBrth = ifelse(yearBrth < 1000, yearBrth + 1000, yearBrth)
         , age = m_year - yearBrth) 
```

```{r, eval = F}
save(gsoep, gsoep_corr, file = sprintf("%s/01_data/01_clean/01_gsoep-clean.RData", wd))
rm(list = ls()[grepl("gsoep", ls())])
```

```{r}
load(sprintf("%s/01_data/01_clean/01_gsoep-clean.RData", wd))
```

### BHPS  
#### Load Data  
```{r bhps clean fun, eval = F}
bhps_read_fun <- function(Year, WL){
  old.names <- (bhps_codebook %>% filter(year == Year | year == 0))$orig_itemname
  keep <- c("SIDp", "pidp", sprintf("%shid", WL))
  sprintf("%s/bhps/%sindresp.sav", data_path, WL) %>% haven::read_sav(.) %>%
    full_join(sprintf("%s/bhps/%shhresp.sav", data_path, WL) %>% haven::read_sav(.)) %>%
    select(one_of(keep), one_of(old.names)) %>%
    haven::zap_labels(.) %>%
    gather(key = orig_itemname, value = value, -one_of(keep), na.rm = T) %>%
    set_names(c("SID", "HHID", "orig_itemname", "value")) %>%
    mutate(value = as.numeric(value))
}
```

```{r bhps codebook}
bhps_codebook <- (codebook %>% filter(study == "bhps"))$codebook[[1]] %>%
  mutate(orig_itemname = str_to_lower(orig_itemname))
bhps_codebook
```

```{r bhps data, eval = F}
bhps_xwaveid <- sprintf("%s/data/bhps/xwaveid.sav", data_path) %>% read_sav()

bhps <- bhps_codebook %>% 
  select(wave, waveletter, year) %>%
  distinct() %>%
  filter(year != 0) %>%
  mutate(data = map2(year, waveletter, bhps_read_fun)) 

bhps_long <- bhps %>% 
  unnest(data) %>% 
  distinct()

save(bhps, file = sprintf("%s/01_data/01_clean/02_bhps-raw.RData", wd))
rm(bhps)
```

#### Recoding  
```{r bhps recode, eval = F}
# join data with recoding info 
bhps_recode <- bhps_codebook %>%
  filter(category %in% c("overall", "domain", "correlates")) %>%
  select(category, name, itemname, wave, year, orig_itemname, reverse_code:recode, mini, maxi, comp_rule, long_rule) %>%
  group_by(category, name) %>% 
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% left_join(bhps_long))) 

# recode 
recode_fun <- function(rule, y, year){
  x <- y$value
  if(!is.na(rule)){y$value <- eval(parse(text = rule))}
  return(y)
}

bhps_recode <- bhps_recode %>% 
  mutate(data = map(data, ~(.) %>% 
    group_by(recode, year) %>%
    nest() %>%
    ungroup() %>%
    mutate(data = pmap(list(recode, data, year), recode_fun)) %>%
    unnest(data) %>%
    mutate(value = ifelse(value < 0 | is.nan(value) | is.infinite(value), NA, value))))


# reverse code 
bhps_recode <- bhps_recode %>%
  mutate(data = map(data, ~(.) %>%
    mutate(value = ifelse(reverse_code == "no" | is.na(reverse_code), value, 
                        reverse.code(-1, value, mini = mini, maxi = maxi)))))

fun_call <- function(x, rule){
    switch(rule,
           average = mean(x, na.rm = T),
           mode = Mode(x)[1],
           sum = sum(x, na.rm = T),
           skip = unique(x)[1],
           select = unique(x)[1],
           max = max(x, na.rm = T),
           min = min(x, na.rm = T))
  }
```

#### Satisfaction  
```{r, eval = F}
bhps <- bhps_recode %>%
  filter(category != "correlates") %>%
  unnest(data) %>%
  select(name, year, SID, value) %>%
  filter(complete.cases(.)) %>%
  group_by(name, year, SID) %>%
  summarize(value = mean(value)) %>%
  ungroup() %>%
  pivot_wider(names_from = "name", values_from = "value") %>%
  group_by(SID) %>%
  filter(n() >= 5) %>%
  ungroup()

bhps_years <- bhps %>%
  group_by(SID) %>%
  filter(year == median(year)) %>%
  ungroup() %>%
  select(m_year = year, SID)
```

#### Correlates  

```{r, eval = F}
bhps_corr <- bhps_recode %>%
  filter(category == "correlates") %>%
  select(-category) %>%
  unnest(data) %>%
  mutate(year = ifelse(name == "parEdu", 0, year)) %>%
  group_by(name) %>% nest() %>% ungroup() %>%
  mutate(data = map(data, ~(.) %>% 
      filter(!is.na(value)) %>%
      mutate(comp_rule = ifelse(is.na(comp_rule), "skip", comp_rule)) %>%
      group_by(comp_rule, SID, year, long_rule) %>%
      nest() %>%
      ungroup() %>%
      mutate(data = map2(data, comp_rule, ~fun_call((.x)$value, .y))) %>%
      unnest(data) %>%
      right_join(bhps_years) %>%
      filter(year <= m_year)
      # summarize(value = fun_call(value, comp_rule)) %>%
      # ungroup() %>% 
      # mutate(value = ifelse(is.infinite(value) | is.nan(value), NA, value))
      ))

comp_fun <- function(d, rule, p_year){
  print(paste(rule, p_year))
  d %>%
    group_by(SID, name) %>%
    summarize(value = fun_call(data, rule)) %>%
    ungroup() %>%
    distinct()
}

# composite ACROSS years
bhps_corr <- bhps_corr %>%
  unnest(data) %>%
  mutate(long_rule = ifelse(is.na(long_rule), "skip", long_rule)) %>%
  filter(year <= m_year) %>%
  group_by(m_year, long_rule) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = pmap(list(data, long_rule, m_year), comp_fun)) %>%
  unnest(data) %>%
  mutate(value = ifelse(is.infinite(value) | is.nan(value), NA, value)) %>%
  select(-long_rule) %>%
  spread(name, value) %>%
  filter(!is.na(SID))%>%
  mutate(yearBrth = ifelse(yearBrth < 1000, yearBrth + 1000, yearBrth)
         , age = m_year - yearBrth) 
```

```{r, eval = F}
save(bhps, bhps_corr, file = sprintf("%s/01_data/01_clean/02_bhps-clean.RData", wd))
rm(list = ls()[grepl("bhps", ls())])
```

```{r bhps load}
load(sprintf("%s/01_data/01_clean/02_bhps-clean.RData", wd))
```


### SHP  
#### Load Data  
```{r shp clean fun, eval = F}
shp_read_fun <- function(x){
  if(grepl("SHP0_BV", x)){old.names <- str_to_lower(old.names)}
  y <- sprintf("%s/shp/%s", data_path, x) %>% haven::read_sav(.) %>%
    haven::zap_labels(.) %>% select(one_of(old.names))
  if(grepl("SHP0_BV", x)){colnames(y) <- str_to_upper(colnames(y))}
  return(y)
} 
```

```{r shp codebook}
shp_codebook <- (codebook %>% filter(study == "shp"))$codebook[[1]] %>%
  filter(year <= 2017 | is.na(year) | year == 0)
shp_codebook
```

```{r shp data, eval = F}
old.names <- unique(shp_codebook$orig_itemname) %>% str_to_upper
datasets <- sprintf("%s/shp", data_path) %>% list.files()
shp <- tibble(datasets = datasets) %>%
  mutate(data = map(datasets, shp_read_fun),
         ncol = map(data, ncol)) %>% 
  unnest(ncol) %>%
  filter(ncol > 1)

shp_grid <- shp %>% filter(datasets == "SHP_MH.sav")
shp <- shp %>% filter(datasets != "SHP_MH.sav")

shp <- reduce(shp$data, full_join) %>% haven::zap_labels(.)

shp_long <- shp %>%
  select(-contains("IDHOUS")) %>%
  pivot_longer(cols = -IDPERS, names_to = "orig_itemname", values_to = "value", values_drop_na = T)

save(shp, file = sprintf("%s/01_data/01_clean/shp_raw.RData", wd))
rm(shp)
```

#### Recoding  
```{r shp recode, eval = F}
# join data with recoding info 
shp_recode <- shp_codebook %>%
  filter(category %in% c("overall", "domain", "correlates")) %>%
  select(category, name, itemname, wave, year, orig_itemname, reverse_code:recode, maxi, mini, comp_rule, long_rule) %>%
  group_by(category, name) %>% 
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% left_join(shp_long %>% rename(SID = IDPERS)))) 

# recode 
recode_fun <- function(rule, y, year){
  yearBrth <- y$yearBrth
  x <- y$value
  if(!is.na(rule)){y$value <- eval(parse(text = rule))}
  return(y)
}

shp_yearbrth <- shp_recode %>% 
  filter(name == "yearBrth") %>%
  unnest(data) %>%
  group_by(SID) %>%
  summarize(yearBrth = Mode(value)) %>%
  ungroup()

shp_recode <- shp_recode %>%
  mutate(data = map(data, ~(.) %>% 
    left_join(shp_yearbrth) %>%
    group_by(recode, year) %>%
    nest() %>%
    ungroup() %>%
    mutate(data = pmap(list(recode, data, year), recode_fun)) %>%
    unnest(data) %>%
    mutate(value = ifelse(value < 0 | is.nan(value) | is.infinite(value), NA, value)) %>%
    select(-yearBrth)))

# reverse code 
shp_recode <- shp_recode %>%
  mutate(data = map(data, ~(.) %>%
    mutate(value = ifelse(reverse_code == "no" | is.na(reverse_code), value, 
                        reverse.code(-1, value, mini = mini, maxi = maxi)))))

fun_call <- function(x, rule){
    switch(rule,
           average = mean(x, na.rm = T),
           mode = Mode(x)[1],
           sum = sum(x, na.rm = T),
           skip = unique(x)[1],
           select = unique(x)[1],
           max = max(x, na.rm = T),
           min = min(x, na.rm = T))
  }
```

#### Satisfaction  
```{r, eval = F}
shp <- shp_recode %>%
  filter(category != "correlates") %>%
  unnest(data) %>%
  select(name, year, SID, value) %>%
  filter(complete.cases(.)) %>%
  group_by(name, year, SID) %>%
  summarize(value = mean(value)) %>%
  ungroup() %>%
  pivot_wider(names_from = "name", values_from = "value") %>%
  group_by(SID) %>%
  filter(n() >= 5) %>%
  ungroup()

shp_years <- shp %>%
  group_by(SID) %>%
  filter(year == median(year)) %>%
  ungroup() %>%
  select(m_year = year, SID)
```

#### Correlates  

```{r, eval = F}
shp_corr <- shp_recode %>%
  filter(category == "correlates") %>%
  select(-category) %>%
  unnest(data) %>%
  mutate(year = ifelse(name == "parEdu", 0, year)) %>%
  group_by(name) %>% nest() %>% ungroup() %>%
  mutate(data = map(data, ~(.) %>% 
      filter(!is.na(value)) %>%
      mutate(comp_rule = ifelse(is.na(comp_rule), "skip", comp_rule)) %>%
      group_by(comp_rule, SID, year, long_rule) %>%
      nest() %>%
      ungroup() %>%
      mutate(data = map2(data, comp_rule, ~fun_call((.x)$value, .y))) %>%
      unnest(data) %>%
      right_join(shp_years) %>%
      filter(year <= m_year)
      # summarize(value = fun_call(value, comp_rule)) %>%
      # ungroup() %>% 
      # mutate(value = ifelse(is.infinite(value) | is.nan(value), NA, value))
      ))

comp_fun <- function(d, rule, p_year){
  print(paste(rule, p_year))
  d %>%
    group_by(SID, name) %>%
    summarize(value = fun_call(data, rule)) %>%
    ungroup() %>%
    distinct()
}

# composite ACROSS years
shp_corr <- shp_corr %>%
  unnest(data) %>%
  mutate(long_rule = ifelse(is.na(long_rule), "skip", long_rule)) %>%
  filter(year <= m_year) %>%
  group_by(m_year, long_rule) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = pmap(list(data, long_rule, m_year), comp_fun)) %>%
  unnest(data) %>%
  mutate(value = ifelse(is.infinite(value) | is.nan(value), NA, value)) %>%
  select(-long_rule) %>%
  spread(name, value) %>%
  filter(!is.na(SID))%>%
  mutate(yearBrth = ifelse(yearBrth < 1000, yearBrth + 1000, yearBrth)
         , age = m_year - yearBrth) 
```

```{r, eval = F}
save(shp, shp_corr, file = sprintf("%s/01_data/01_clean/03_shp-clean.RData", wd))
rm(list = ls()[grepl("shp", ls())])
```

```{r shp load}
load(sprintf("%s/01_data/01_clean/03_shp-clean.RData", wd))
```

### LISS  
#### Load Data  
```{r liss clean fun, eval = F}
liss_read_fun <- function(x){
  sprintf("%s/liss/%s", data_path, x) %>% haven::read_sav(.) %>% select(one_of(old.names))
}
```

```{r liss codebook}
liss_codebook <- (codebook %>% filter(study == "liss"))$codebook[[1]]
liss_codebook
```

```{r liss data, eval = F}
old.names <- unique(liss_codebook$orig_itemname) %>% str_to_lower
datasets <- sprintf("%s/liss", data_path) %>% list.files()
liss <- tibble(datasets = datasets) %>%
  mutate(data = map(datasets, liss_read_fun)) 

liss <- reduce(liss$data, full_join) %>% haven::zap_labels(.)
save(liss, file = sprintf("%s/01_data/01_clean/04_liss-raw.RData", wd))

avars <- tibble(ds = datasets[grepl("avar", datasets)]) %>%
  mutate(data = map(ds, ~sprintf("%s/liss/%s", data_path, .) %>% haven::read_sav(.) %>% select(one_of(old.names)) %>% haven::zap_labels(.))) %>%
  separate(ds, c("ds", "year", "scrap1", "scrap2"), sep = "_") %>%
  separate(year, c("year", "month"), -2) %>%
  select(year, month, data) %>% 
  unnest(data) %>%
  pivot_longer(cols = c(burgstat, geslacht, belbezig, gebjaar)
               , names_to = "orig_itemname"
               , values_to = "value"
               , values_drop_na = T) %>%
  group_by(orig_itemname, nomem_encr, year) %>%
  summarize(value = Mode(value)) %>%
  ungroup()

liss_long <- liss %>%
  pivot_longer(cols = -nomem_encr
               , names_to = "orig_itemname"
               , values_to = "value"
               , values_drop_na = T) %>%
  left_join(liss_codebook %>% select(orig_itemname, year)) %>%
  full_join(avars %>% mutate(year = as.numeric(year)))
```

#### Recoding  
```{r, eval = F} 
rename_fun <- function(df){
  df %>% left_join(liss_long %>% rename(SID = nomem_encr))
}

# join data with recoding info 
liss_recode <- liss_codebook %>%
  filter(category %in% c("overall", "domain", "correlates")) %>%
  select(category, name, itemname, wave, year, orig_itemname, reverse_code:recode, mini, maxi, comp_rule, long_rule) %>%
  distinct() %>%
  group_by(category, name, mini, maxi) %>% 
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, rename_fun)) 

# recode 
recode_fun <- function(rule, y, year){
  x <- y$value
  if(!is.na(rule)){y$value <- eval(parse(text = rule))}
  return(y)
}

liss_recode <- liss_recode %>% 
  mutate(data = map(data, ~(.) %>% 
    group_by(recode, year) %>%
    nest() %>%
    ungroup() %>%
    mutate(data = pmap(list(recode, data, year), recode_fun)) %>%
    unnest(data) %>%
    mutate(value = ifelse(value < 0 | is.nan(value) | is.infinite(value), NA, value))))

rev_code_fun <- function(df, mini, maxi){
  df %>%
    mutate(value = ifelse(reverse_code == "no" | is.na(reverse_code), value, 
                        reverse.code(-1, value, mini = mini, maxi = maxi)))
}

# reverse code 
liss_recode <- liss_recode %>%
  mutate(data = pmap(list(data, mini, maxi), rev_code_fun))

fun_call <- function(x, rule){
    switch(rule,
           average = mean(x, na.rm = T),
           mode = Mode(x)[1],
           sum = sum(x, na.rm = T),
           skip = unique(x)[1],
           select = unique(x)[1],
           max = max(x, na.rm = T),
           min = min(x, na.rm = T))
  }
```

#### Satisfaction  
```{r liss restructuring, eval = F}
pomp_fun <- function(d, mini, maxi){
  d %>%
     mutate(value = ((value - mini)/(maxi-mini))*10) # pomp)
}

liss <- liss_recode %>%
  filter(category != "correlates") %>%
  mutate(data = pmap(list(data, mini, maxi), pomp_fun)) %>%
  unnest(data) %>%
  select(name, year, SID, value) %>%
  filter(complete.cases(.)) %>%
  group_by(name, year, SID) %>%
  summarize(value = mean(value)) %>%
  ungroup() %>%
  pivot_wider(names_from = "name", values_from = "value") %>%
  group_by(SID) %>%
  filter(n() >= 5) %>%
  ungroup()

liss_years <- liss %>%
  group_by(SID) %>%
  filter(year == median(year)) %>%
  ungroup() %>%
  select(m_year = year, SID)
```

#### Correlates  

```{r, eval = F}
liss_corr <- liss_recode %>%
  filter(category == "correlates") %>%
  select(-category) %>%
  unnest(data) %>%
  mutate(year = ifelse(name == "parEdu", 0, year)) %>%
  group_by(name) %>% nest() %>% ungroup() %>%
  mutate(data = map(data, ~(.) %>% 
      filter(!is.na(value)) %>%
      mutate(comp_rule = ifelse(is.na(comp_rule), "skip", comp_rule)) %>%
      group_by(comp_rule, SID, year, long_rule) %>%
      nest() %>%
      ungroup() %>%
      mutate(data = map2(data, comp_rule, ~fun_call((.x)$value, .y))) %>%
      unnest(data) %>%
      right_join(liss_years) %>%
      filter(year <= m_year)
      # summarize(value = fun_call(value, comp_rule)) %>%
      # ungroup() %>% 
      # mutate(value = ifelse(is.infinite(value) | is.nan(value), NA, value))
      ))

comp_fun <- function(d, rule, p_year){
  print(paste(rule, p_year))
  d %>%
    group_by(SID, name) %>%
    summarize(value = fun_call(data, rule)) %>%
    ungroup() %>%
    distinct()
}

# composite ACROSS years
liss_corr <- liss_corr %>%
  unnest(data) %>%
  mutate(long_rule = ifelse(is.na(long_rule), "skip", long_rule)) %>%
  filter(year <= m_year) %>%
  group_by(m_year, long_rule) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = pmap(list(data, long_rule, m_year), comp_fun)) %>%
  unnest(data) %>%
  mutate(value = ifelse(is.infinite(value) | is.nan(value), NA, value)) %>%
  select(-long_rule) %>%
  spread(name, value) %>%
  filter(!is.na(SID))%>%
  mutate(yearBrth = ifelse(yearBrth < 1000, yearBrth + 1000, yearBrth)
         , age = m_year - yearBrth) 
```

```{r, eval = F}
save(liss, liss_corr, file = sprintf("%s/01_data/01_clean/04_liss-clean.RData", wd))
rm(list = ls()[grepl("liss", ls())])
```


```{r liss load}
load(sprintf("%s/01_data/01_clean/04_liss-clean.RData", wd))
```

### HILDA  
#### Load Data  
```{r hilda clean fun, eval = F}
hilda_read_fun <- function(Year, WL){
  old.names <- (hilda_codebook %>% filter(year == Year | year == 0))$orig_itemname
  sprintf("%s/hilda/Combined %s180c.sav", data_path, WL) %>% haven::read_sav(.) %>%
    select(one_of(old.names)) 
}
```

```{r hilda codebook}
hilda_codebook <- (codebook %>% filter(study == "hilda"))$codebook[[1]]
hilda_codebook
```

```{r hilda data, eval = F}
hilda <- hilda_codebook %>% 
  select(year, wave_letter) %>%
  filter(!is.na(wave_letter)) %>%
  distinct() %>%
  mutate(wave_letter = tolower(wave_letter), 
         data = map2(year, wave_letter, hilda_read_fun)) 

save(hilda, file = sprintf("%s/01_data/01_clean/hilda_raw.RData", wd))
```

#### Recoding  
```{r hilda recode, eval = F}
rename_fun <- function(df, Year){
  df <- df %>%
    haven::zap_labels(.) %>%
    gather(key = orig_itemname, value = value, -xwaveid, na.rm=T) %>%
    mutate(value=as.numeric(value))
  hilda_codebook %>% 
    select(category, name, itemname, year, orig_itemname, recode, reverse_code, mini, maxi, comp_rule, long_rule) %>%
    filter(year == Year & category %in% c("overall", "domain", "correlates")) %>%
    full_join(df)
}

# join data with recoding info 
hilda_recode <- hilda %>%
  mutate(data = map2(data, year, rename_fun)) %>% 
  select(-year, -wave_letter) %>%
  unnest(data) %>%
  distinct() %>%
  rename(SID = xwaveid) %>%
  group_by(category, name) %>%
  nest() %>% 
  ungroup()

# recode 
recode_fun <- function(rule, y, year){
  x <- y$value
  if(!is.na(rule)){y$value <- eval(parse(text = rule))}
  return(y)
}

hilda_recode <- hilda_recode %>% 
  mutate(data = map(data, ~(.) %>% 
    group_by(recode, year) %>%
    nest() %>%
    ungroup() %>%
    mutate(data = pmap(list(recode, data, year), recode_fun)) %>%
    unnest(data) %>%
    mutate(value = ifelse(value < 0 | is.nan(value) | is.infinite(value), NA, value))))

fun_call <- function(x, rule){
    switch(rule,
           average = mean(x, na.rm = T),
           mode = Mode(x)[1],
           sum = sum(x, na.rm = T),
           skip = unique(x)[1],
           select = unique(x)[1],
           max = max(x, na.rm = T),
           min = min(x, na.rm = T))
  }
```

#### Satisfaction  
```{r hilda restructuring, eval = F}
hilda <- 
    hilda_recode %>%
      filter(category != "correlates") %>%
      unnest(data) %>%
      select(name, year, SID, value) %>%
      filter(complete.cases(.)) %>%
      group_by(name, year, SID) %>%
      summarize(value = mean(value)) %>%
      ungroup() %>%
      pivot_wider(names_from = "name", values_from = "value") %>%
  group_by(SID) %>%
  filter(n() >= 5) %>%
  ungroup()

hilda_years <- hilda %>%
  group_by(SID) %>%
  filter(year == median(year)) %>%
  ungroup() %>%
  select(m_year = year, SID)
```

#### Correlates  

```{r, eval = F}
hilda_corr <- hilda_recode %>%
  filter(category == "correlates") %>%
  select(-category) %>%
  mutate(data = map(data, ~(.) %>% 
      filter(!is.na(value)) %>%
      mutate(comp_rule = ifelse(is.na(comp_rule), "skip", comp_rule)) %>%
      group_by(comp_rule, SID, year, long_rule) %>%
      nest() %>%
      ungroup() %>%
      mutate(data = map2(data, comp_rule, ~fun_call((.x)$value, .y))) %>%
      unnest(data) %>%
      right_join(hilda_years) %>%
      filter(year <= m_year)
      ))

comp_fun <- function(d, rule, p_year){
  print(paste(rule, p_year))
  d %>%
    group_by(SID, name) %>%
    summarize(value = fun_call(data, rule)) %>%
    ungroup() %>%
    distinct()
}

# composite ACROSS years
hilda_corr <- hilda_corr %>%
  unnest(data) %>%
  mutate(long_rule = ifelse(is.na(long_rule), "skip", long_rule)) %>%
  filter(year <= m_year) %>%
  group_by(m_year, long_rule) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = pmap(list(data, long_rule, m_year), comp_fun)) %>%
  unnest(data) %>%
  mutate(value = ifelse(is.infinite(value) | is.nan(value), NA, value)) %>%
  select(-long_rule) %>%
  spread(name, value) %>%
  filter(!is.na(SID))%>%
  mutate(yearBrth = ifelse(yearBrth < 1000, yearBrth + 1000, yearBrth)
         , age = m_year - yearBrth) 
```

```{r}
save(hilda, hilda_corr, file = sprintf("%s/01_data/01_clean/05_hilda-clean.RData", wd))
rm(list = ls()[grepl("hilda", ls())])
```


```{r hilda load}
load(sprintf("%s/01_data/01_clean/05_hilda-clean.RData", wd))
```

# Zero Order Relationships  
```{r zero-order relationships}
r_fun <- function(dat){
  dat <- dat %>% ungroup()
  r <- cor(dat %>% select(-SID), use = "pairwise")
  r[upper.tri(r, diag = T)] <- NA
  nvar <- nrow(r)
  tab <- data.frame(r) %>% mutate(v1 = paste(1:nvar, ". ", rownames(.), sep = "")) %>% 
    select(v1, everything(), -age) %>%
    full_join(dat %>% select(-SID) %>% gather(key = v1, value = value) %>%
                group_by(v1) %>%
                summarize(mean = mean(value, na.rm = T), sd = sd(value, na.rm = T)) %>%
                ungroup() %>%
                mutate(v1 = factor(v1, levels = colnames(r))) %>% 
                arrange(v1) %>%
                mutate(v1 = paste(1:nvar, ". ", v1, sep = ""))) %>%
    setNames(c("v1", 1:(nvar-1), "M", "SD")) %>%
    mutate_at(vars(`1`:SD), ~ifelse(!is.na(.) == T, sprintf("%.2f", .), ""))
  
  tab$M[grepl("gender", tab$v1)] <- paste(sprintf("%.2f", table(dat$gender)[1]/sum(table(dat$gender))), " %", sep = "")
  tab$SD[grepl("gender", tab$v1)] <- ""
  return(tab)
}

rs <- tibble(
  dataset = c("GSOEP", "SHP", "BHPS", "LISS"), 
  data = list(
    gsoep %>% filter(year == 1985) %>% select(SID, amtleis, health:work, gender, age),
    shp %>% filter(year == 2001) %>% select(SID, amtleis, health:lifesat, social:work, gender, age),
    bhps %>% filter(year == 1996) %>% select(SID, amtleis:work, gender, age),
    liss %>% filter(year == 2008) %>% select(SID, amtleis:work, gender, age)
    )
) %>%
  mutate(r = map(data, r_fun))
```


# Population Networks
## Model Function  
```{r mlvar functions}
mlVAR_call <- function(d, study, type){
  mlVAR_fun(d, study, type, 1)
  # mlVAR_fun(d, study, type, 2)
  return(NULL)
}

mlVAR_fun <- function(d, study, type, lag){
  vs <- colnames(d %>% select(-SID, -year))
  m <- mlVAR(
    d
    , vars = vs
    , idvar = "SID"
    , lags = lag
    # , beepvar = "year"
    , temporal = "orthogonal"
    , contemporaneous = "orthogonal"
    , verbose = TRUE
    , scale = F
  )
  save(m, file = sprintf("%s/04_results/01_mlVAR/%s-%s-lag%s.RData"
                         , wd, study, type, lag))
  return(NULL)
}
```

## Run Models  
```{r run mlvar}
prep_fun <- function(d){
  cutoff <- 5
  na_test <- apply(d, 2, function(x) sum(!is.na(x)))
  if(any(na_test < cutoff)) return(NA) else return(d)
}

net_nested <- tibble(Study = rep(c("GSOEP", "SHP", "BHPS", "LISS", "HILDA"), each = 2)
       , hrmnzn = rep(c("Harmonized", "Unharmonized"), times = 5)
       , data = list(
         gsoep   %>% select(SID, year, amtleis, health:house, income:work)
         , gsoep %>% select(SID, year, amtleis:work)
         , shp   %>% select(SID, year, amtleis, health:house, income:lifesat, work)
         , shp   %>% select(SID, year, amtleis:income, social:work)
         , bhps  %>% select(SID, year, amtleis:lifesat, work)
         , bhps  %>% select(SID, year, amtleis:work)
         , liss  %>% select(SID, year, amtleis, house:lifesat, work)
         , liss  %>% select(SID, year, amtleis:work)
         , hilda %>% select(SID, year, amtleis, health:house, income:lifesat, work)
         , hilda %>% select(SID, year, amtleis:work)
       )
) %>%
  filter(hrmnzn == "Harmonized") %>%
  mutate(data = map(data, ~(.)  %>% 
      mutate(SID = as.character(SID)) %>% 
      arrange(SID, year) %>% 
      group_by(SID) %>% 
      nest() %>% 
      ungroup() %>%
      mutate(data = map(data, prep_fun)) %>%
      filter(!is.na(data))))

rm(list = ls()[!ls() %in% c("data_path", "mlVAR_call", "mlVAR_fun", "net_nested", "wd")])
gc()

net_nested <- net_nested %>% 
  filter(Study == "LISS") %>%
  mutate(data = map(data, ~(.) %>% 
                      mutate(data = map(data, ~(.) %>% filter(complete.cases(.)))) %>%
                      filter(map_dbl(data, nrow) >= 6) %>%
                      unnest(data) %>%
                      arrange(SID, year)),
         m = pmap(list(data, Study, hrmnzn), mlVAR_call))
```

## Load Results  
```{r}
loadRData <- function(fileName, type){
#loads an RData file, and returns it
    path <- sprintf("%s/04_results/01_mlVAR/%s", wd, fileName)
    load(path)
    get(ls()[ls() == type])
}

net_nested <- tibble(file = sprintf("%s/04_results/01_mlVAR", wd) %>% list.files()) %>%
  filter(!grepl("pop_", file)) %>%
  mutate(m = map(file, ~loadRData(., "m"))) %>%
  separate(file, c("Study", "hrmnzn", "lag"))
```


## Plots  
```{r}
plot_fun <- function(x, type, sd = F, sig = "hide", study, h, lag){
  groups <- list(
    lifesat = which(x$fit$var == "lifesat")
    , other = seq(1:nrow(x$fit))[-which(x$fit$var == "lifesat")]
    )
  ttl <- sprintf("\n%s: %s %s", study, h, lag)
  plot.res <- plot(x
                   , type
                   , layout = "spring"
                   , groups = groups
                   , nonsig = sig
                   , curve = -1
                   , legend = FALSE
                   , SD = sd
                   , details = FALSE
                   , mar = rep(10, 4)
                   , border.width = 2.5
                   # , title =  ttl
                   # , threshold = .01
                   , loop = .7
                   , node.width = 1.6
                   , edge.width = 1
                   , asize = 5
                   , label.font = 2
                   , label.fill.vertical = 1
                   , label.fill.horizontal = 1
                   , edge.color = "blue"
                   , DoNotPlot = TRUE
                   , color = c(RColorBrewer::brewer.pal(3, "Set3")[1], "white")
                   )
  if(sd == F){
  plot.res$graphAttributes$Edges$lty[plot.res$Edgelist$weight < 0] <- 2
  plot.res$graphAttributes$Edges$color <-
    ifelse(plot.res$Edgelist$weight <.02, "thistle2",
    ifelse(plot.res$Edgelist$weight <.04, "mediumorchid", "midnightblue"))
  }
  # plot(plot.res); title(ttl)
  return(list(p = plot.res, ttl = ttl))
}

net_nested <- net_nested %>%
  mutate(plot = pmap(list(x = m, type = "temporal", sd = F, sig = "hide", study = Study, h = hrmnzn, lag = lag)
                     , plot_fun))

plot_print <- function(l){
  plot(l$p); title(l$ttl)
}

pdf(file = sprintf("%s/04_results/04_figures/fig-1-mlVARs.pdf", wd)
    , width = 8, height = 6)
par(mfrow = c(2,3), oma=c(0,0,2,0))
net_nested %>% mutate(p = map(plot, plot_print))
dev.off()
```

## Structure Comparisons
### Full Models
```{r}
net_nested <- net_nested %>%
  mutate(summary = map(m, ~summary(.))
         , lagged = map(summary, ~(.)$temporal))

lagged_edges <- net_nested %>% 
  select(Study, hrmnzn, lagged) %>%
  unnest(lagged) %>%
  select(from, to, fixed, Study) %>%
  spread(key = Study, value = fixed) %>%
  unite(path, from, to, sep = "->")
lagged_mat <- lagged_edges %>% select(-path) %>% as.matrix()
rownames(lagged_mat) <- lagged_edges$path

r <- cor(lagged_mat, use = "pairwise")
r[upper.tri(r, diag = T)] <- NA
r[lower.tri(r, diag = F)] <- sprintf("%.2f", r[lower.tri(r, diag = F)])
diag(r) <- "--"
r %>% data.frame() %>% rownames_to_column("Study") %>%
  kable(., "html"
        , caption = "Cross-Study Structure Comparisons of Harmonized, Lag 1 Pathways") %>%
  kable_styling(full_width = F)
```

## Centrality  
```{r}
net_nested <- net_nested %>%
  mutate(centrality = map(lagged, ~centrality_auto((.) %>% filter(P < .05) %>% select(from, to, fixed)))
         , centrality = map(centrality, ~(.)$node.centrality)
         , cent_plot = map(lagged, ~centralityPlot((.) %>% select(from, to, fixed))))
```

```{r}
save(net_nested, file = sprintf("%s/04_results/01_mlVAR/pop_results.RData", wd))
net_nested <- net_nested %>% select(Study, hrmnzn, plot, lagged, centrality, cent_plot)
save(net_nested, file = sprintf("%s/04_results/01_mlVAR/pop_results_small.RData", wd))
```


# Person Level
## Run Models
```{r, eval = F}
idio_nested <- tibble(Study = rep(c("GSOEP", "SHP", "BHPS", "LISS", "HILDA"), each = 2)
       , hrmnzn = rep(c("Harmonized", "Unharmonized"), times = 5)
       , data = list(
         gsoep   %>% select(SID, year, amtleis, health:house, income:work)
         , gsoep %>% select(SID, year, amtleis:work)
         , shp   %>% select(SID, year, amtleis, health:house, income:lifesat, work)
         , shp   %>% select(SID, year, amtleis:income, social:work)
         , bhps  %>% select(SID, year, amtleis:lifesat, work)
         , bhps  %>% select(SID, year, amtleis:work)
         , liss  %>% select(SID, year, amtleis, house:lifesat, work)
         , liss  %>% select(SID, year, amtleis:work)
         , hilda %>% select(SID, year, amtleis, health:house, income:lifesat, work)
         , hilda %>% select(SID, year, amtleis:work)
       )
) %>%
  mutate(data = map(data, ~(.) %>% arrange(SID, year) %>% select(-year) %>% group_by(SID) %>% nest() %>% ungroup())) %>%
  unnest(data) %>%
  filter(map_dbl(data, nrow) >= 8)

gVAR_fun <- function(d, SID, study, type, perc){
  print(sprintf("%s Subject %s, %.2f complete", study, SID, perc))
  n <- nrow(d)
  cutoff <- ifelse(study == "GSOEP", 15, 5)
  na_test <- apply(d, 2, function(x) sum(is.na(x) == F))
  sd_test <- apply(d, 2, function(x) sd(x, na.rm = T) == 0)
  na_test <- which(na_test < cutoff | sd_test == TRUE)
  if(length(na_test >= 1)){d <- select(d, -na_test)}
  # dat <- dat[complete.cases(dat),]
  gamma <- 0; lambda <- seq(.01, n*.01, length.out = 10) #c(n*01, n*.02) 
  fit <-
    graphicalVAR(d
                 , gamma = gamma
                 , maxit.in = 1000
                 , maxit.out = 1000
                 , lambda_beta = lambda
                 , lambda_kappa = lambda[1]
                 , verbose = T
                 , scale = F
                 , centerWithin = F
                 , likelihood = "unpenalized"
                 )
  save(fit, file = sprintf("%s/04_results/02_graphicalVAR/models/%s/%s/%s.RData"
                           , wd, type, study, SID))
  fit <- list(PCC = fit$PCC, PDC = fit$PDC)
  save(fit, file = sprintf("%s/04_results/02_graphicalVAR/small/%s/%s/%s.RData"
                           , wd, type, study, SID))
  gc()
  return(T)
}
# done <- crossing(Study = c("GSOEP", "BHPS", "SHP")
#                  , hrmnzn = c("Harmonized", "Unharmonized")) %>%
#   mutate(path = sprintf("%s/04_results/02_graphicalVAR/models/%s/%s",wd, hrmnzn, Study),
#          SID = map(path, list.files)) %>%
#   select(-path) %>%
#   unnest(SID) %>%
#   mutate(SID = as.numeric(str_remove_all(SID, ".RData"))
#          , done = "done")
# plan(multiprocess(workers = 3L))
net_nested <- net_nested %>%
  # full_join(done) %>%
  # filter(is.na(done)) %>%
  arrange(hrmnzn, Study) %>%
  filter(row_number() %in% 1:1000) %>%
  mutate(perc = row_number()/n()*100) %>%
  filter(!(Study == "BHPS" & SID %in% 
    c("28575", "149611", "276767", "280165", "300567", "410051", "499811"))) %>%
  mutate(gVAR_fit = 
           # future_pmap(
           pmap(
             list(data, SID, Study, hrmnzn, perc)
             , possibly(gVAR_fun, NA_real_)
             # , .options = furrr_options(
             #   globals = c("gVAR_fun", "wd")
             #   , packages = c("plyr", "tidyverse", "graphicalVAR")
             #   )
             )
         )
# closeAllConnections()
```

## Load Results 
```{r}
loadRData <- function(fileName, type, study){
#loads an RData file, and returns it
    path <- sprintf("%s/04_results/02_graphicalVAR/small/Harmonized/%s/%s", wd, study, fileName)
    load(path)
    get(ls()[ls() == type])
}

idio_nested <- tibble(Study = c("BHPS", "GSOEP", "HILDA", "LISS", "SHP")
       , SID = map(Study, ~list.files(sprintf("%s/04_results/02_graphicalVAR/small/Harmonized/%s", wd, .)))) %>%
  unnest(SID) %>%
  mutate(m = map2(SID, Study, ~loadRData(.x, "fit", .y)),
         SID = str_remove_all(SID, ".RData"))
```

## Extract Coefficients  
```{r}
beta_fun <- function(fit, SID){
  PDC <- fit$PDC
  from <- row.names(PDC)
  PDC.long <- tbl_df(PDC) %>%
    mutate(from = from,
           type = "Temporal") %>%
    gather(key = to, value = weight, everything(), -from, -type)
}

kappa_mat_fun <- function(fit){fit$PCC}

kappa_long_fun <- function(fit){
  PCC <- fit$PCC
  PCC[lower.tri(PCC, diag = T)] <- NA
  vars <- rownames(PCC)
  PCC.long <- tbl_df(PCC) %>%
    mutate(Var1 = vars,
           type = "Contemporaneous") %>%
    gather(key = Var2, value = weight, -Var1, -type) %>%
    filter(!is.na(weight)) %>%
    unite(var, Var1, Var2, sep = ".", remove = F)
}

idio_nested <- idio_nested %>%
  filter(!is.na(m)) %>%
  mutate(beta = map2(m, SID, beta_fun),
         kappa_mat = map(m, kappa_mat_fun),
         kappa = map(m, kappa_long_fun))
```

##Structure Comparisons
```{r}
profile_cor_fun <- function(id, study){
  id <- id %>% 
    select(SID, from, to, weight) %>%
    unite(path, from, to, sep = "->") %>%
    pivot_wider(names_from = "SID", values_from = "weight")
  pop <- lagged_edges %>% 
    select(path, one_of(study))
  full <- id %>% full_join(pop)
  cor(full %>% select(-path, -contains(study))
      , full %>% select(contains(study))
      , use = "pairwise") %>%
    data.frame() %>%
    setNames("r") %>%
    rownames_to_column("SID") %>%
    as_tibble()
}

edge_fun <- function(id, study){
  id_mat <- id %>% 
    select(SID, from, to, weight) %>%
    unite(path, from, to, sep = "->") %>%
    pivot_wider(names_from = "SID", values_from = "weight")
  pop_mat <- net_nested %>%
    filter(Study == study) %>%
    select(lagged) %>%
    unnest(lagged) %>% 
    mutate(fixed = ifelse(P < .05, fixed, 0)) %>% 
    unite(path, from, to, sep = "->") %>%
    select(path, pop = fixed) 
  full_mat <- id_mat %>% full_join(pop_mat)
  res <- sapply(full_mat %>% select(-path, -pop), function(x) {
    nEdges <- length(x)
    nEdgesOrig <- sum(full_mat$pop != 0, na.rm = T)
    nShared <- sum(full_mat$pop != 0 & x != 0, na.rm = T)
    nMissing <- sum(full_mat$pop == 0 & x == 0, na.rm = T) # missing edges
    tibble(prop_shared = nShared/nEdgesOrig,
         prop_missing = nMissing/(nEdges  - nEdgesOrig),
         prop_repl = prop_shared + prop_missing)
  }) %>%
    t() %>%
    data.frame() %>%
    rownames_to_column("SID") %>%
    as_tibble() %>%
    unnest(cols = c(prop_shared, prop_missing, prop_repl))
  return(res)
}

cong_procors <- idio_nested %>%
  select(Study, SID, beta) %>%
  group_by(Study) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% unnest(beta)),
         temp_procor = map2(data, Study, profile_cor_fun),
         temp_match = map2(data, Study, edge_fun))
cong_procors <- cong_procors %>% select(-data)
save(cong_procors, file = sprintf("%s/04_results/congruence_cor.RData", wd))

cong_procor <- cong_procors %>% 
  select(-data) %>%
  unnest(temp_procor) 

cong_procor %>%
  group_by(Study) %>%
  summarise(mean = fisherz2r(mean(fisherz(r), na.rm = T)),
            sd = fisherz2r(sd(fisherz(r), na.rm = T)),
            max = max(r, na.rm = T), 
            min = min(r, na.rm = T),
            median = median(r, na.rm = T))

cong_procor %>%
  ggplot(aes(x = r, y = Study, fill = Study)) + 
  # geom_density(color = "black", alpha = .25) +
    ggridges::geom_density_ridges(alpha = .5) + 
    geom_vline(aes(xintercept = 0), linetype = "dashed") + 
    # facet_grid(.~Study) +  +
    scale_x_continuous(limits = c(-1,1), breaks = seq(-1,1,1)) +
    labs(x = "Correlation", y = NULL) +
    theme_classic() + 
    theme(legend.position = "none"
          , axis.text = element_text(face = "bold", size = rel(1.5))
          , axis.title = element_text(face = "bold", size = rel(1.5)))

ggsave(sprintf("%s/04_results/04_figures/congruence_cor.pdf", wd), width = 6, height = 9)
```

## Centrality  
```{r}
centrality_direction <- function(edge_list, type){
  if(type == "temporal"){
    varnames <- unique(edge_list$from)
    df <- tbl_df(matrix(rep(NA, 9 * length(varnames)), ncol = 9)) %>%
      setNames(c("var", "inDegreeNeg", "inDegreePos", "inStrengthNeg", "inStrengthPos",
                 "outDegreeNeg", "outDegreePos", "outStrengthNeg", "outStrengthPos"))
    for(i in 1:length(varnames)){
      var1 <- varnames[i]
      df[i,] <- edge_list %>% 
        filter(from == var1 | to == var1) %>%
        mutate(direction = ifelse(from == var1, "out", "in"),
               Variable = var1) %>%
        group_by(direction, Variable) %>%
        summarize(StrengthPos = sum(weight[weight > 0], na.rm = T),
                  StrengthNeg = sum(weight[weight < 0], na.rm = T),
                  DegreePos = sum(weight > 0),
                  DegreeNeg = sum(weight < 0)) %>%
        gather(key = type, value = value, StrengthPos:DegreeNeg) %>%
        unite(comb, direction, type, sep = "") %>%
        spread(key = comb, value = value)
    }
    return(df)
  } else {
    varnames <- unique(c(edge_list$Var1, edge_list$Var2))
    df <- tbl_df(matrix(rep(NA, 3 * length(varnames)), ncol = 5)) %>%
      setNames(c("Variable", "Negative", "Positive"))
    for(i in 1:length(varnames)){
      var1 <- varnames[i]
      df[i,] <- edge_list %>% 
        filter(Var1 == var1 | Var2 == var1) %>%
        mutate(Variable = var1) %>%
        group_by(Variable) %>%
        summarize(Positive = sum(weight[weight > 0], na.rm = T),
                  Negative = sum(weight[weight < 0], na.rm = T))
    }
    return(df)
  }
}

centralityList <- function(x, gVAR, SID, dataset) {
  print(sprintf("%s Subject %s", as.character(dataset), SID))
      centrality <- centrality_auto(data.frame(select(x, from, to, weight)))
      mat <- gVAR$PDC
      diag(mat) <- 0
      varnames <- as.character(unique(x$from))
      degree <- tibble(var = row.names(mat), 
                       InDegree = colSums(mat != 0), 
                       OutDegree = rowSums(mat != 0))
      df <- tbl_df(centrality$node.centrality %>% mutate(var = varnames)) %>%
      full_join(degree)
      return(df)
}

beta_centrality_fun <- function(x) {
  data <- x %>%
    select(from, to, weight) %>%
    mutate(weight = as.numeric(weight))
  centrality <- centrality_auto(data.frame(data))
  outdegree <- degree(igraph::as.igraph(qgraph(data, DoNotPlot = TRUE), attributes = TRUE), mode = c("out"))
  indegree <- degree(igraph::as.igraph(qgraph(data, DoNotPlot = TRUE), attributes = TRUE), mode = c("in"))
  df <- data.frame(var = rownames(centrality$node.centrality), 
                   centrality$node.centrality,
                   InDegree = indegree,
                   OutDegree = outdegree,
                   Degree = indegree + outdegree)
}
```

```{r, eval = F}
# calculate centrality for each subject for each wave and save them to a list #
idio_nested <- idio_nested %>%
  mutate(#beta_centrality = map(beta, possibly(beta_centrality_fun, NA_real_)), 
         #beta_signed_centrality = map(beta, possibly(~centrality_direction(., "temporal"), NA_real_)),
         beta_centrality = pmap(list(beta, m, SID, Study), 
                                centralityList))
save(idio_nested, file = sprintf("%s/04_results/02_graphicalVAR/idio_nested.RData", wd))
idio_plots <- idio_nested %>% select(Study, SID, temp_plot, beta_centrality)
save(idio_plots, file = sprintf("%s/04_results/02_graphicalVAR/idio_plots.RData", wd))
```

```{r}
beta_centrality <- idio_nested %>%
  filter(!is.na(beta_centrality)) %>%
  select(Study, SID, beta_centrality) %>%
  unnest(beta_centrality) %>%
  mutate(type = "Lagged") %>%
  select(Study, SID, type, var, InStrength, OutStrength, InDegree, OutDegree) %>%
  gather(key = measure, value = value, InStrength, OutStrength, na.rm = T) %>%
  group_by(measure, SID, Study) %>%
  mutate(asc_rank = dense_rank(desc(value)),
         desc_rank = dense_rank(value),
         z = as.numeric(scale(value, center = T, scale = T))) %>%
  ungroup() %>%
  group_by(measure, var, Study) %>%
  mutate(rank_var = dense_rank(desc(value))) %>% 
  ungroup()

# beta_signed_centrality <- net_nested %>%
#   unnest(beta_signed_centrality) %>%
#   mutate(type = "Temporal",
#          SID = factor(SID)) %>%
#   gather(key = measure, value = value, contains("Strength")) %>%
#   group_by(measure, SID, dataset) %>%
#   mutate(asc_rank = dense_rank(desc(value)),
#          desc_rank = dense_rank(value),
#          z = as.numeric(scale(value))) %>%
#   ungroup()

# Top Down Only
pure_top_down_SID <- beta_centrality %>%
  filter(var == "lifesat" & measure %in% c("InStrength", "OutStrength") &
        (OutDegree >= 4 & InDegree == 0) &
        (asc_rank[measure == "OutStrength"] %in% 1 & abs(z) > 1) &
        (desc_rank[measure == "InStrength"] %in% 1 & abs(z) > 1)) %>%
  mutate(group = "top down")

# Bottom Up
pure_bottom_up_SID <- beta_centrality %>%
  filter(var == "lifesat" & measure %in% c("InStrength", "OutStrength") &
        (InDegree >= 4 & OutDegree == 0) &
        (desc_rank[measure == "OutStrength"] %in% 1 & abs(z) > 1) &
        (asc_rank[measure == "InStrength"] %in% 1 & abs(z) > 1)) %>%
  mutate(group = "bottom up")

both_SID <- beta_centrality %>%
  filter(var == "lifesat" & measure %in% c("InStrength", "OutStrength") &
        (OutDegree >= 3 & InDegree >= 3) &
        (asc_rank[measure == "OutStrength"] %in% 1:2 & abs(z) > 1) &
        (asc_rank[measure == "InStrength"] %in% 1:2 & abs(z) > 1)) %>%
  mutate(group = "both")

neither_SID <- beta_centrality %>%
  filter(var == "lifesat" & measure %in% c("InStrength", "OutStrength") &
        (OutDegree < 2 & InDegree < 2) &
        (desc_rank[measure == "OutStrength"] %in% 1 & abs(z) > 1) &
        (desc_rank[measure == "InStrength"] %in% 1 & abs(z) > 1)) %>%
  mutate(group = "neither")
```



##Plots
```{r, eval = F}
edge_colors <- RColorBrewer::brewer.pal(8, "Purples")[c(3,5,7)]
plot_fun <- function(data, SID, type, dataset){
  x <- if(type == "Temporal") data$PDC else data$PCC
  # nvar <- dim(data_mod)[2]
  groups <- list(
    lifesat = which(rownames(x) == "lifesat")
    , other = seq(1:nrow(x))[-which(rownames(x) == "lifesat")]
    )
  plot <- qgraph(x
                 , layout = "spring"
                 , title = sprintf("%s: %s for S%s", dataset, type, SID)
                 , loop = .7
                 , node.width = 1.4
                 , edge.width = 1
                 , label.font = 2
                 , label.fill.vertical = 1
                 , label.fill.horizontal = 1
                 , edge.color = "black"
                 , groups = groups
                 , color = c(RColorBrewer::brewer.pal(3, "Set3")[1], "white")
                 , legend = F
                 , DoNotPlot = TRUE
                 , mar = c(4,4,4,4)
                 , asize = 6
                 , border.width = 2.5
                 )
  plot$graphAttributes$Edges$lty[plot$Edgelist$weight < 0] <- 2
  plot$graphAttributes$Edges$color <-
    ifelse(abs(plot$Edgelist$weight) <.1, edge_colors[1],
    ifelse(abs(plot$Edgelist$weight) <.2, edge_colors[2], edge_colors[3]))
  return(plot)
}

library(animation)
idio_nested <- idio_nested %>%
  mutate(
    temp_plot = pmap(
      list(m, SID, "Temporal", Study)
      , possibly(plot_fun, NA_real_)
      ),
    contemp_plot = pmap(
      list(m, SID, "Contemporaneous", Study)
      , possibly(plot_fun, NA_real_))
    )
save(idio_nested, file = sprintf("%s/04_results/02_graphicalVAR/idio_nested.RData", wd))
```

### GIFS  
```{r}
setwd("~/Box/network/other projects/swb networks/04_results/04_figures/01_gifs")
library(animation)
draw.a.plot <-  function(x){
  plot(temp_plots[[x]])
}

# Pure Top Down - Highest in OutStrength, Lowest in InStrength
loop.animate <- function() {
    lapply(names(temp_plots), function(i) {draw.a.plot(i)})
}

gif_fun <- function(d, study){
  temp_plots <- d$temp_plot
  names(temp_plots) <- d$SID
  temp_plots <- temp_plots[sample(d$SID, 100)]
  saveGIF(loop.animate()
          , interval = 2
          , movie.name = sprintf("%s/04_results/04_figures/01_gifs/%s_full.gif", wd, study)
          , ani.width = 500
          , ani.height = 500
          )
}

idio_nested %>%
  select(Study, SID, temp_plot) %>%
  group_by(Study) %>%
  nest() %>%
  ungroup() %>%
  mutate(p = map2(data, Study, gif_fun))

# Pure Bottom Up - Highest in InStrength, Lowest in OutStrength
loop.animate <- function() {
    lapply(as.character((pure_bottom_up_SID %>% filter(dataset == "GSOEP"))$SID), function(i) {
       draw.a.plot(i) })
}
saveGIF(loop.animate(), interval = 2, movie.name="gsoep_bottom_up_beta_plots.gif", ani.width = 500, ani.height = 500)


# Pure Top Down - Highest in OutStrength, Lowest in InStrength
loop.animate <- function() {
    lapply(as.character((both_SID %>% filter(dataset == "GSOEP"))$SID), function(i) {
       draw.a.plot(i) })
}
saveGIF(loop.animate(), interval = 2, movie.name="gsoep_mixed_bottom_top_beta_plots.gif", ani.width = 500, ani.height = 500)

# Pure Bottom Up - Highest in InStrength, Lowest in OutStrength
loop.animate <- function() {
    lapply(as.character((neither_SID %>% filter(dataset == "GSOEP"))$SID), function(i) {
       draw.a.plot(i) })
}
saveGIF(loop.animate(), interval = 2, movie.name="gsoep_weird_independent_beta_plots.gif", ani.width = 500, ani.height = 500)
```

```{r}
idio_nested %>%
  filter(!is.na(beta_centrality)) %>%
  select(Study, SID, beta_centrality) %>%
  unnest(beta_centrality) %>%
  mutate(type = "Temporal") %>%
  group_by(SID, Study) %>%
  mutate_at(vars(InStrength, OutStrength), funs(z = as.numeric(scale(.)))) %>%
  ungroup() %>%
  filter(var == "lifesat") %>%
  ggplot(aes(x = InStrength_z, y = OutStrength_z)) + 
    # geom_hex() +
  stat_density2d(aes(fill = ..level..), geom = "polygon", n = 100) +#, h = .2) +
  # geom_density_2d() +
  xlim(c(-2.5,2.5)) + ylim(c(-2.5,2.5)) +
  geom_hline(aes(yintercept = 0)) + 
  geom_vline(aes(xintercept = 0)) +
  annotate("text", x = -2.5, y = -2.5, label = "Neither", hjust = 0) +
  annotate("text", x = -2.5, y =  2.5, label = "Top Down", hjust = 0) +
  annotate("text", x =  2.5, y = -2.5, label = "Bottom Up", hjust = 1) +
  annotate("text", x =  2.5, y =  2.5, label = "Both", hjust = 1) +
  labs(x = "Standardized In Strength (Domain \u2192 General)", y = "Standardized Out Strength\n(General \u2192 Domain)",
       fill = "Density") +
  facet_grid(.~Study) + 
  theme_classic() +
  theme(plot.title  = element_text(face = "bold", hjust = .5),
        axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold"),
        legend.position = "bottom", 
        strip.text = element_text(face = "bold", size = rel(1.2)))
ggsave(file = sprintf("%s/04_results/04_figures/fig-4-density.pdf", wd)
       , width = 12, height = 5)
```

## Top Down v. Bottom Up Comparisons  

### GSOEP  
```{r}
comp_fun <- function(beta){
  vars <- unique(beta$from)
  beta <- beta %>% 
    filter((from == "lifesat" | to == "lifesat") & from != to) %>%
    mutate(direction = ifelse(from == "lifesat", "topdown", "bottomup"),
           var = ifelse(direction == "topdown", to, from)) %>%
    select(-(from:to)) %>%
    spread(key = direction, value = weight) %>%
    mutate(diff = topdown-bottomup)
  return(beta)
}

idio_nested <- idio_nested %>%
  mutate(diff = map(beta, possibly(comp_fun, NA_real_)))

idio_nested %>%
  select(Study, SID, diff) %>%
  unnest(diff) 

beta_centrality %>%
  filter(var == "lifesat" & 
        (measure == "InStrength" | measure == "OutStrength")) %>%
  select(SID, measure, value, Study) %>%
  spread(key = measure, value = value) %>%
  right_join(
    idio_nested %>% select(Study, SID, diff) %>% unnest(diff) 
  ) %>%
  ggplot(aes(x = InStrength, y = OutStrength, fill = diff)) + 
  geom_raster() + 
  facet_wrap(Study~var)
```


# Correlates  

## Data Setup  
```{r}
data_setup_fun <- function(d, study){
  vars <- c("DEP", "grsWages", "occPrstg", "PhysFunc", "SRhealth", "SS", "loneliness")
  cols <- vars[vars %in% colnames(d)]
  d %>% 
    mutate_at(vars(all_of(cols)), ~as.numeric(scale(.))) %>%
    mutate(age = age - 35,
           education = education - 12,
           SID = as.character(SID)) %>%
    pivot_longer(cols = - SID
                 , names_to = "o_name"
                 , values_to = "o_value"
                 , values_drop_na = T) %>%
    right_join(beta_centrality %>% 
                 filter(Study == study & var == "lifesat" & 
                          (measure == "InStrength" | measure == "OutStrength")) %>%
                 select(SID, measure, z)) %>%
    group_by(o_name, measure) %>%
    nest() %>%
    ungroup()
}


nested_corr <- tribble(
  ~Study, ~data, 
  "BHPS" , bhps_corr  %>% select(-m_year, -yearBrth),
  "GSOEP", gsoep_corr %>% select(-m_year, -yearBrth),
  "HILDA", hilda_corr %>% select(-m_year, -yearBrth),
  "LISS" , liss_corr  %>% select(-m_year, -yearBrth),
  "SHP"  , shp_corr   %>% select(-m_year, -yearBrth)
) %>%
  mutate(data = map2(data, Study, data_setup_fun)) %>%
  unnest(data) %>%
  group_by(o_name, measure) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% unnest(data)))

save_fun <- function(d, o, m){
  save(d, file = sprintf("%s/01_data/02_correlates/%s_%s.RData", wd, o, m))
  return(NULL)
}

nested_corr %>% mutate(s = pmap(list(data, o_name, measure), save_fun))
```

## Zero-Order  
```{r}
corr_fun <- function(d){
  r <- cor.ci(d %>% select(-SID), use = "pairwise")
  r2 <- print(r) %>%
    data.frame() %>%
    rownames_to_column("path") %>%
    filter(grepl("InStr", path) | grepl("OtStr", path)) %>%
    separate(path, c("o_name", "measure"), sep = "-") %>%
    filter(!(o_name == "InStr" & measure == "OtStr")) %>%
    select(o_name, measure, lower.emp, upper.emp)
  return(r2)
}

nested_zero_corr <- nested_corr %>% 
  unnest(data) %>%
  # filter(!is.na(o_name)) %>%
  pivot_wider(names_from = "o_name"
              , values_from = "o_value") %>%
  pivot_wider(names_from = "measure"
              , values_from = "z") %>%
  group_by(Study) %>%
  nest() %>%
  ungroup() %>%
  mutate(r = map(data, corr_fun))

nested_zero_corr %>%
  select(-data) %>%
  unnest(r) %>%
  filter(sign(lower.emp) == sign(upper.emp))
```


## Initialize Models  
```{r}
load(sprintf("%s/01_data/02_correlates/DEP_InStrength.RData", wd))
Prior <-  c(set_prior("cauchy(0,1)", class = "sd"),
              set_prior("student_t(3, 0, 2)", class = "b"),
              set_prior("student_t(3, 0, 5)", class = "Intercept"))
Iter <- 2000; Warmup <- 1000; treedepth <- 20
d <- d %>%
   group_by(Study) %>%
   nest() %>%
   ungroup() %>%
   mutate(data = map(data, ~(.) %>% filter(row_number() %in% sample(1:nrow(.), 100, replace = F)))) %>%
   unnest(data)

init <- brm(formula = z ~ o_value + (1 + o_value | Study)
             , data = d
             , iter = Iter
             , warmup = Warmup
             , cores = 8
           )
save(init, file = sprintf("%s/04_results/05_correlates/brms_small_cont.RData", wd))

load(sprintf("%s/01_data/02_correlates/gender_InStrength.RData", wd))
d <- d %>%
  group_by(Study, o_value) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% filter(row_number() %in% sample(1:nrow(.), 50, replace = F)))) %>%
  unnest(data) %>%
  mutate(o_value = as.factor(o_value))

init <- brm(formula = z ~ o_value + (1 + o_value | Study)
             , data = d
             , iter = Iter
             , warmup = Warmup
             , cores = 8
           )
save(init, file = sprintf("%s/04_results/05_correlates/brms_small_fac.RData", wd))
rm(list = c("init", "Prior", "Warmup", "d"))
```


## Model Function  

```{r}
brms_call <- function(outcome, measure){
  # load the data
  load(sprintf("%s/01_data/02_correlates/%s_%s.RData", wd, outcome, measure))
  
  # load the compiled brms models and factorize categorical variables
  if(outcome %in%  c("DEP", "grsWages", "occPrstg", "PhysFunc", "SRhealth", "SS"
                     , "age", "education", "CC", "numKids", "loneliness")){
    load(sprintf("%s/04_results/05_correlates/brms_small_cont.RData", wd))
  } else{
    load(sprintf("%s/04_results/05_correlates/brms_small_fac.RData", wd))
    d <- d %>% mutate(o_value = factor(o_value))
  }
  
  # set the priors
  Prior <-  c(set_prior("cauchy(0,1)", class = "sd"),
              set_prior("student_t(3, 0, 2)", class = "b"),
              set_prior("student_t(3, 0, 5)", class = "Intercept"))
  
  # fit the model by updating the compiled model with new, full data sets
  fit <- update(init
                , newdata = d
                , iter = 3000
                , warmup = 1000
                # , prior = Prior
                , cores = 12)
  save(fit, file = sprintf("%s/04_results/05_correlates/01_models/%s_%s.RData", wd, outcome, measure))
  
  # get model coefficients
  fx <- broom.mixed::tidy(fit, probs = c(0.025, 0.975))
  save(fx, file = sprintf("%s/04_results/05_correlates/02_fx/%s_%s.RData", wd, outcome, measure))
  
  # get study-specific effects
  rx <- ranef(init, probs = c(0.025, 0.975))[[1]] %>% array_tree(3) %>%
    tibble(names = names(.), data = .) %>%
    mutate(data = map(data, ~(.) %>% data.frame %>%
                        rownames_to_column("Study"))) %>%
    unnest(data) %>%
    as_tibble()
  save(rx, file = sprintf("%s/04_results/05_correlates/03_rx/%s_%s.RData", wd, outcome, measure))
  
  # clean up the environment
  rm(list = c("d", "init", "fit", "fx", "rx"))
  gc()
  return(T)
}
```

## Run Models  
```{r, eval = F}
tibble(file = sprintf("%s/01_data/02_correlates", wd) %>% list.files()) %>%
  # full_join(tibble(file = sprintf("%s/04_results/05_correlates/01_models", wd) %>% list.files(), done = "done")) %>%
  # filter(is.na(done)) %>%
  separate(file, c("o_name", "measure", "scrap")) %>%
  filter(o_name %in% c("loneliness", "PhysFunc", "numKids")) %>%
  mutate(m = map2(o_name, measure, possibly(brms_call, NA_real_)))
```

## Compile Results  
```{r}
loadRData <- function(fileName, type){
    dir <- if(type == "fx") "02_fx" else "03_rx"
#loads an RData file, and returns it
    path <- sprintf("%s/04_results/05_correlates/%s/%s", wd, dir, fileName)
    load(path)
    get(ls()[ls() == type])
}

nested_corr <-tibble(file = sprintf("%s/04_results/05_correlates/02_fx", wd) %>% list.files()) %>%
  separate(file, c("o_name", "measure", "scrap"), remove = F) %>%
  mutate(fx = map(file, ~loadRData(., "fx")),
         rx = map(file, ~loadRData(., "rx"))) %>%
  select(-file, -scrap)
```

## Overall  
```{r}
nested_corr %>%
  select(-rx) %>%
  unnest(fx) %>%
  filter(grepl("o_value", term) & effect == "fixed") %>%
  select(-effect, -component, -group, -std.error) %>%
  mutate(sig = ifelse(sign(conf.low) == sign(conf.high), "sig", "ns")
         , CI = sprintf("[%.2f, %.2f]", conf.low, conf.high)
         , b = sprintf("%.2f", estimate)) %>%
  mutate_at(vars(b, CI), ~ifelse(sig == "sig", sprintf("<strong>%s</strong>", .), .)) %>%
  select(o_name, measure, term, b, CI) %>%
  pivot_wider(names_from = "measure"
              , values_from = c("b", "CI")
              , names_glue = "{measure}_{.value}")
```

```{r}
nested_corr %>%
  select(-fx) %>%
  unnest(rx) %>%
  filter(grepl("o_value", names)) %>%
  select(-Est.Error) %>%
  mutate(sig = ifelse(sign(Q2.5) == sign(Q97.5), "sig", "ns")
         , CI = sprintf("[%.2f, %.2f]", Q2.5, Q97.5)
         , b = sprintf("%.2f", Estimate)) %>%
  mutate_at(vars(b, CI), ~ifelse(sig == "sig", sprintf("<strong>%s</strong>", .), .)) %>%
  select(o_name, measure, term = names, b, CI)
```

